rang

### 2023-07-20 paper/basel2023_rang/index.qmd
Correct typos
Say more in the last slide
Trim slides

## Computational reproducibility

|                        | **Same Data** | **Different Data** |
|------------------------|---------------|--------------------|
| **Same Analysis**      | Reproducible  | Replicable         |
| **Different Analysis** | Robust        | Generalisable      |

::: {style="font-size: 0.3em"}

Source: [The Turing Way](https://the-turing-way.netlify.app/reproducible-research/overview/overview-definitions.html)

:::

@@

:::{.column width="50%"}

![](bowie.jpg)

(1947.01.08 - 2016.01.10)
:::

:::{.column width="50%"}

@@

:::

@@

```{.r code-line-numbers="|1|2"}
p3m <- "https://packagemanager.posit.co/cran/2016-01-10"
options(repos = c(REPO_NAME = p3m))
install.packages("dplyr") # install 0.4.3?

@@

```{.r code-line-numbers="|3"}
require(renv)
renv::init() ## restart
renv::checkout(date = "2016-01-10") 
install.packages("dplyr")
renv::snapshot()
require(dplyr)
data <- data.frame(id = c(1,1,2), outcome = c(TRUE, TRUE, FALSE))
distinct(data, id) %>%
    select(outcome)
```

@@

## Pit shop 1: Summary

@@

It's base.

@@

```bash
docker run --rm -it rocker/r-ver:3.2.0
```

@@

@@

## Pit shop 2: Summary

@@

:::{.column width="80%"}
1. Computational reproducibility is tacitly dependent on the computational environment
2. Use P3M for projects after 2017-10-10
3. Use Rocker for projects newer than R 3.0.0
4. Use `rang` for probably all projects
:::

>>>>

<!-- ## Computational reproducibility -->

<!-- |                        | **Same Data** | **Different Data** | -->
<!-- |------------------------|---------------|--------------------| -->
<!-- | **Same Analysis**      | Reproducible  | Replicable         | -->
<!-- | **Different Analysis** | Robust        | Generalisable      | -->

<!-- ::: {style="font-size: 0.3em"} -->

<!-- Source: [The Turing Way](https://the-turing-way.netlify.app/reproducible-research/overview/overview-definitions.html) -->

<!-- ::: -->

@@

<!-- :::: {.columns} -->

<!-- :::{.column width="50%"} -->

<!-- ![](bowie.jpg) -->

<!-- (1947.01.08 - 2016.01.10) -->
<!-- ::: -->

<!-- :::{.column width="50%"} -->

@@

<!-- ::: -->

<!-- :::: -->

@@

```{.r code-line-numbers="|1|2|"}
p3m <- "https://packagemanager.posit.co/cran/2016-01-10"
options(repos = c(REPO_NAME = p3m))
install.packages("dplyr") # install 0.4.3?

@@

```{.r code-line-numbers="|3|"}
require(renv)
renv::init() ## restart
renv::checkout(date = "2016-01-10") 
install.packages("dplyr")
renv::snapshot()
require(dplyr)
data <- data.frame(id = c(1,1,2), outcome = c(TRUE, TRUE, FALSE))
distinct(data, id) %>%
    select(outcome)
```

@@

## Pit stop 1: Summary

@@

It's base. You can't pin `unix.time()` with P3M/`renv`.

@@

```bash
# work
docker run --rm -it rocker/r-ver:3.0.0
```

@@

```bash
# not work
docker run --rm -it rocker/r-ver:2.15.3
```

@@

## Pit stop 2: Summary

@@

:::{.column width="80%"}
1. Computational reproducibility is tacitly dependent on the computational environment
2. Use P3M / renv for projects after 2017-10-10
    * only at the level of R packages
3. Plus Rocker for projects newer than R 3.0.0
4. Use `rang` for probably all projects
:::
